The Accuracy of KNN, decision tree, random forest, SVM, neural network, naive Bayes classifier and PLA for early Prediction of Diabetes

### 2023-04-05 hw1/paper/main.tex
test B

\section{Experiment result}
  This work compare the common classification algorithms, including KNN (with brute force, ANNOY-DFS, ANNOY-BFS), decision tree, 
  random forest, SVM (modified by GA), Neural Network, Naive Bayes classifier (modified by GA), PLA-pocket algorithm. 
  The programming language of KNN, decision tree, random forest and SVM-GA are C++20. And Neural Network, Naive Bayes classifier-GA 
  and PLA-pocket are using Python3 with pytorch and scikit-learn library. 
  Table \ref{table:overall} compares all datasets, which show that ...
  \begin{table*}[htb]
    %\normalsize
    %\centering
    \newcommand{\z}{\phantom{0}}
    \caption{\textsc{Comparison of Classification Techniques.}}
      \vspace{-\baselineskip}
    \begin{tabular}{@{}lccccccl@{}}\toprule
    Technique & Search (s) & testA & testA-normalized & testB & testB-normalized \\ \midrule
    KNN-Brute-Force  & $0.009$ & $76.6169 \pm \z{0}$                & $80.597 \pm 0$               & $78 \pm \z{0}$                 & $80 \pm \z{0}$\\
    KNN-ANNOY-DFS    & $0.003$ & $75.2438 \pm \z{1.8762}$           & $76.1294 \pm 2.0977$         & $74.9 \pm \z{2.5554}$          & $76.4 \pm \z{2.5377}$\\
    KNN-ANNOY-BFS    & $0.012$ & $76.6567 \pm \z{0.5340}$           & $80.597 \pm 0$               & $78.16 \pm \z{0.7310}$         & $80 \pm \z{0}$\\
    decision tree    & $0.009$ & $74.1294 \pm \z{0}$                & $74.1294 \pm 0$              & $76 \pm \z{0}$                 & $77 \pm \z{0}$\\
    random forest    & $0.004$ & $78.6965 \pm \z{1.751}$            & $78.5373 \pm 1.452$          & $77.98 \pm \z{2.083}$          & $77.5 \pm \z{2.516}$\\
    SVM-GA           & $X$ & $X \pm \z{X}$                          & $X \pm X$                    & $X \pm \z{X}$                  & $X \pm \z{X}$\\
    Neural Network   & $X$ & $X \pm \z{X}$                          & $X \pm X$                    & $X \pm \z{X}$                  & $X \pm \z{X}$\\
    Naive Bayes classifier-GA    & $X$ & $X \pm \z{X}$              & $X \pm X$                    & $X \pm \z{X}$                  & $X \pm \z{X}$\\
    PLA-pocket       & $X$ & $X \pm \z{X}$                          & $X \pm X$                    & $X \pm \z{X}$                  & $X \pm \z{X}$\\ \midrule
    %&& Search (s) & test & Search(s) & test & Search(s) & test \\ \midrule
    \end{tabular}
    \label{table:overall}
      \vspace{-\baselineskip}
  \end{table*}

>>>>

\section{Experiment result}
  This work compare the common classification algorithms, including KNN (with brute force, ANNOY-DFS, ANNOY-BFS), decision tree, 
  random forest, SVM (modified by GA), Neural Network, Naive Bayes classifier (modified by GA), PLA-pocket algorithm. 
  The programming language of KNN, decision tree, random forest and SVM-GA are C++20. And Neural Network, Naive Bayes classifier-GA 
  and PLA-pocket are using Python3 with pytorch and scikit-learn library. 
  Table \ref{table:overall} compares all datasets, which show that ...
  \begin{table*}[htb]
    %\normalsize
    %\centering
    \newcommand{\z}{\phantom{0}}
    \caption{\textsc{Comparison of Classification Techniques.}}
      \vspace{-\baselineskip}
    \begin{tabular}{@{}lccccccl@{}}\toprule
    Technique & Search (s) & testA & testA-normalized & testB & testB-normalized \\ \midrule
    KNN-Brute-Force  & $0.009$ & $76.6169 \pm \z{0}$                & $80.597 \pm 0$               & $78 \pm \z{0}$                 & $80 \pm \z{0}$\\
    KNN-ANNOY-DFS    & $0.003$ & $75.2438 \pm \z{1.8762}$           & $76.1294 \pm 2.0977$         & $74.9 \pm \z{2.5554}$          & $76.4 \pm \z{2.5377}$\\
    KNN-ANNOY-BFS    & $0.012$ & $76.6567 \pm \z{0.5340}$           & $80.597 \pm 0$               & $78.16 \pm \z{0.7310}$         & $80 \pm \z{0}$\\
    decision tree    & $0.009$ & $74.1294 \pm \z{0}$                & $74.1294 \pm 0$              & $76 \pm \z{0}$                 & $77 \pm \z{0}$\\
    random forest    & $0.004$ & $78.6965 \pm \z{1.751}$            & $78.5373 \pm 1.452$          & $77.98 \pm \z{2.083}$          & $77.5 \pm \z{2.516}$\\
    SVM-GA           & $X$ & $X \pm \z{X}$                          & $X \pm X$                    & $X \pm \z{X}$                  & $X \pm \z{X}$\\
    Neural Network   & $3.2$   & $81.7910 \pm \z{2.0294}$           & $80.2985 \pm 1.4106$         & $78 \pm \z{1.6733}$            & $77.5 \pm \z{1.892}$\\
    Naive Bayes classifier-GA    & $X$ & $X \pm \z{X}$              & $X \pm X$                    & $X \pm \z{X}$                  & $X \pm \z{X}$\\
    PLA-pocket       & $X$ & $X \pm \z{X}$                          & $X \pm X$                    & $X \pm \z{X}$                  & $X \pm \z{X}$\\ \midrule
    %&& Search (s) & test & Search(s) & test & Search(s) & test \\ \midrule
    \end{tabular}
    \label{table:overall}
      \vspace{-\baselineskip}
  \end{table*}
